---
output:
  html_notebook: default
  pdf_document: default
  html_document: default
---
# Business Data Analytics and Prediction</br>
**

##  EDA in R 

```{r}
library(ggplot2)
library(plotrix)

```
 
### Create a Test Set

After a quick glance, we splited our data to train and test sets, and then put the test set aside and dont look on it until you have models to compare.

####  Read the data 

The business analytics concepts and code will be demonstrated on fligth delayed and canceled https://www.kaggle.com/giovamata/airlinedelaycauses

We download the csv file from the link above.


and then we read the cvs file in to a data frame, as below.


```{r}
df  = read.csv(file="C:/Users/User/Documents/MBA/semester 1/Bussiness Data Analysics/data/flights/DelayedFlights.csv",header=TRUE,as.is=TRUE,na.strings=c("NA",".",""))
```

####Split the data to train and test


```{r}

set.seed(111)
bound <- floor((nrow(df)/4)*3)
d <- df[sample(nrow(df)), ]
df.train <- d[1:bound, ]
df.test <- d[(bound+1):nrow(df), ]
```


### Explore the data set

```{r}
summary(df.train)

```

```{r}
df.train$WeekDaybyName <- df.train$DayOfWeek
df.train$MonthByName <- df.train$Month

df.train$WeekDaybyName[df.train$WeekDaybyName == 1] = 'Monday'
df.train$WeekDaybyName[df.train$WeekDaybyName == 2] = 'Tuesday'
df.train$WeekDaybyName[df.train$WeekDaybyName == 3] = 'Wednesday'
df.train$WeekDaybyName[df.train$WeekDaybyName == 4] = 'Thursday'
df.train$WeekDaybyName[df.train$WeekDaybyName == 5] = 'Friday'
df.train$WeekDaybyName[df.train$WeekDaybyName == 6] = 'Saturday'
df.train$WeekDaybyName[df.train$WeekDaybyName == 7] = 'Sunday'

df.train$MonthByName[df.train$MonthByName == 1] = 'January'
df.train$MonthByName[df.train$MonthByName == 2] = 'February'
df.train$MonthByName[df.train$MonthByName == 3] = 'March'
df.train$MonthByName[df.train$MonthByName == 4] = 'April'
df.train$MonthByName[df.train$MonthByName == 5] = 'May'
df.train$MonthByName[df.train$MonthByName == 6] = 'June'
df.train$MonthByName[df.train$MonthByName == 7] = 'July'
df.train$MonthByName[df.train$MonthByName == 8] = 'August'
df.train$MonthByName[df.train$MonthByName == 9] = 'September'
df.train$MonthByName[df.train$MonthByName == 10] = 'October'
df.train$MonthByName[df.train$MonthByName == 11] = 'November'
df.train$MonthByName[df.train$MonthByName == 12] = 'December'
```


We have removed the information that is missing data

```{r}

(nrow(df.train ) - nrow(df.train [complete.cases(df.train ),]))/nrow(df.train )

df.train.complete  <- df.train [complete.cases(df.train ),]
sam.df.train.complete <- df.train.complete [sample(nrow(df.train.complete  ), 10000),]
```

```{r}

summary(df.train.complete)
```
We see that when we remove the missing information we have no more information about the cancellations 
```{r}

CancelledSubset = subset(df.train, CancellationCode != 'N')
df.train$CancellationCodebyname <- df.train$CancellationCode 
df.train$CancellationCodebyname[df.train$CancellationCodebyname == 'A'] = 'Carrier'
df.train$CancellationCodebyname[df.train$CancellationCodebyname == 'B'] = 'Weather'
df.train$CancellationCodebyname[df.train$CancellationCodebyname == 'C'] = 'NAS'
df.train$CancellationCodebyname[df.train$CancellationCodebyname == 'D'] = 'Security'



ggplot(CancelledSubset,aes(MonthByName,fill=CancellationCodebyname)) + geom_bar()



```

#### Draw the histogram 



```{r}
maxfer= nrow(df.train.complete)
par(mfrow = c(2,4) ); 
hist(df.train.complete$ArrDelay,          main = "Arrval Delay ", border = "blue", col = "light blue", breaks = 100, xlim=c(0,300))
hist(df.train.complete$DepDelay,          main = "Depart Delay ", border = "blue", col = "light blue", breaks = 100, xlim=c(0,300))
hist(df.train.complete$CarrierDelay,      main = "Carrier Delay", border = "blue", col = "light blue", breaks = 100, xlim=c(0,300))
hist(df.train.complete$WeatherDelay,      main = "Weather Delay.", border = "blue", col = "light blue", breaks = 100, xlim=c(0,300))
hist(df.train.complete$NASDelay,          main = "NAS Delay.", border = "blue", col = "light blue", breaks = 100,  xlim=c(0,300))
hist(df.train.complete$SecurityDelay,     main = "Security Delay.", border = "blue", col = "light blue", breaks = 100, xlim=c(0,300))
hist(df.train.complete$LateAircraftDelay, main = "Late Aircraft Delay.", border = "blue", col = "light blue", breaks = 100, xlim=c(0,300))


```


```{r}
h0 <- hist(df.train.complete$ArrDelay,breaks=300, plot = FALSE)
h1 <- hist(df.train.complete$DepDelay,breaks=300, plot = FALSE) 

plot(h0, main = "Histogram of Arrival and Departure Delay ", col = rgb(0,0,1, alpha = 0.5), xlim = c(0,300))  #plot the first hist
plot(h1, col = rgb(1,0,0, alpha = 0.5), add = TRUE,xlim = c(0,300)) #add the second hist
legend("right", c( "Arrival Delay","Departure Delay"), fill = c("blue","red"), cex=0.8) #Legend

```

```{r}
library("limma")

hdnas<-logical(nrow(df.train.complete))
hdcar<-logical(nrow(df.train.complete))
hdwat<-logical(nrow(df.train.complete))
hdsec<-logical(nrow(df.train.complete))
hdlat<-logical(nrow(df.train.complete))

hdnas[which(df.train.complete$NASDelay>=15)]         =TRUE
hdcar[which(df.train.complete$CarrierDelay>=15)]     =TRUE
hdwat[which(df.train.complete$WeatherDelay>=15)]     =TRUE 
hdsec[which(df.train.complete$SecurityDelay>=15)]    =TRUE
hdlat[which(df.train.complete$LateAircraftDelay>=15)]=TRUE 

c5 <- cbind(hdnas, hdcar , hdwat , hdsec ,hdlat)


a <- vennCounts(c5)
vennDiagram(a, include = "both",
            names = c("NAS Delay", "Carrier Delay", "Weather Delay","Security Delay","Late Aircraft Delay"),
            counts.col = "red")
```
```{r}
num_of_NAS_only     = length(which(df.train.complete$NASDelay>=15 & df.train.complete$SecurityDelay==0 & df.train.complete$WeatherDelay==0 & df.train.complete$CarrierDelay ==0 & df.train.complete$LateAircraftDelay==0))
num_of_securit      = length(which(df.train.complete$NASDelay==0 & df.train.complete$SecurityDelay>=15 & df.train.complete$WeatherDelay==0 & df.train.complete$CarrierDelay ==0 & df.train.complete$LateAircraftDelay==0)) 
num_of_WeatherDelay = length(which(df.train.complete$NASDelay==0 & df.train.complete$SecurityDelay==0 & df.train.complete$WeatherDelay>=15 & df.train.complete$CarrierDelay ==0 & df.train.complete$LateAircraftDelay==0)) 
num_of_CarrierDelay = length(which(df.train.complete$NASDelay==0 & df.train.complete$SecurityDelay==0 & df.train.complete$WeatherDelay==0 & df.train.complete$CarrierDelay >=15 & df.train.complete$LateAircraftDelay==0)) 
num_of_LateAircraf  = length(which(df.train.complete$NASDelay==0 & df.train.complete$SecurityDelay==0 & df.train.complete$WeatherDelay==0 & df.train.complete$CarrierDelay ==0 & df.train.complete$LateAircraftDelay>=15)) 




slices <- c(num_of_WeatherDelay,num_of_NAS_only,num_of_securit ,num_of_CarrierDelay,num_of_LateAircraf)
lbls   <- c("Weather","NAS_only","Security","Carrier","Late Air craft")

pie(slices, labels = lbls, main="Pie Chart delay")
```
```{r}
non_char_list=which(lapply(df.train,typeof)!="character")
cor_list<-c(3,6,7,8,9,13,14,15,16,17,20,21,22)
pairs(sam.df.train.complete[as.numeric(cor_list)],col = "blue", cex = 0.5, upper.panel = NULL)
```



```{r}

ggplot(df.train.complete, aes(x=CRSElapsedTime, y=ActualElapsedTime))+geom_point(alpha=0.3, colour="blue")+geom_abline(colour="red", intercept=0, slope=1)
```


### Regretion 

```{r}

cor(df.train.complete$AirTime,df.train.complete$ActualElapsedTime)
rg_airTime_lm=lm(formula=df.train.complete$ActualElapsed~df.train.complete$AirTime)
summary(rg_airTime_lm)
```

```{r}
ggplot(df.train.complete, aes(x=AirTime, y=ActualElapsedTime))+geom_point(alpha=0.3, colour="blue")+geom_abline(colour="red", intercept= as.double(rg_airTime_lm$coefficients[1]), slope= as.double(rg_airTime_lm$coefficients[2]))
```
```{r}
cor(df.train.complete$AirTime,df.train.complete$Distance)
rg_airTime_lm=lm(formula=df.train.complete$AirTime~ df.train.complete$Distance)
summary(rg_airTime_lm)
```

```{r}
ggplot(df.train.complete, aes(x=Distance,y=AirTime))+geom_point(alpha=0.3, colour="blue")+geom_abline(colour="red", intercept= as.double(rg_airTime_lm$coefficients[1]), slope= as.double(rg_airTime_lm$coefficients[2]))

```

```{r}

var <- c("ActualElapsedTime","AirTime", "TaxiOut","TaxiIn")

toReg <- sam.df.train.complete[,var]
reg <- lm(ActualElapsedTime~., data= toReg)

summary(reg)
``````

