---
output:
  html_notebook: default
  pdf_document: default
  html_document: default
---
# Business Data Analytics and Prediction</br>
**

##  EDA in R 

```{r}
library(ggplot2)
library(plotrix)

```
 
### Create a Test Set

After a quick glance, we splited our data to train and test sets, and then put the test set aside and dont look on it until you have models to compare.

####  Read the data 

The business analytics concepts and code will be demonstrated on fligth delayed and canceled https://www.kaggle.com/giovamata/airlinedelaycauses

We download the csv file from the link above.


and then we read the cvs file in to a data frame, as below.


```{r}
df  = read.csv(file="C:/Users/User/Documents/MBA/semester 1/Bussiness Data Analysics/data/flights/DelayedFlights.csv",header=TRUE,as.is=TRUE,na.strings=c("NA",".",""))
```

####Split the data to train and test


```{r}

set.seed(111)
bound <- floor((nrow(df)/4)*3)
d <- df[sample(nrow(df)), ]
df.train <- d[1:bound, ]
df.test <- d[(bound+1):nrow(df), ]
```


### Explore the data set

```{r}
summary(df.train)

```

```{r}
df.train$WeekDaybyName <- df.train$DayOfWeek
df.train$MonthByName <- df.train$Month

df.train$WeekDaybyName[df.train$WeekDaybyName == 1] = 'Monday'
df.train$WeekDaybyName[df.train$WeekDaybyName == 2] = 'Tuesday'
df.train$WeekDaybyName[df.train$WeekDaybyName == 3] = 'Wednesday'
df.train$WeekDaybyName[df.train$WeekDaybyName == 4] = 'Thursday'
df.train$WeekDaybyName[df.train$WeekDaybyName == 5] = 'Friday'
df.train$WeekDaybyName[df.train$WeekDaybyName == 6] = 'Saturday'
df.train$WeekDaybyName[df.train$WeekDaybyName == 7] = 'Sunday'

df.train$MonthByName[df.train$MonthByName == 1] = 'January'
df.train$MonthByName[df.train$MonthByName == 2] = 'February'
df.train$MonthByName[df.train$MonthByName == 3] = 'March'
df.train$MonthByName[df.train$MonthByName == 4] = 'April'
df.train$MonthByName[df.train$MonthByName == 5] = 'May'
df.train$MonthByName[df.train$MonthByName == 6] = 'June'
df.train$MonthByName[df.train$MonthByName == 7] = 'July'
df.train$MonthByName[df.train$MonthByName == 8] = 'August'
df.train$MonthByName[df.train$MonthByName == 9] = 'September'
df.train$MonthByName[df.train$MonthByName == 10] = 'October'
df.train$MonthByName[df.train$MonthByName == 11] = 'November'
df.train$MonthByName[df.train$MonthByName == 12] = 'December'
```


We have removed the information that is missing data

```{r}

(nrow(df.train ) - nrow(df.train [complete.cases(df.train ),]))/nrow(df.train )

df.train.complete  <- df.train [complete.cases(df.train ),]
sam.df.train.complete <- df.train.complete [sample(nrow(df.train.complete  ), 10000),]
```

```{r}

summary(df.train.complete)
```
We see that when we remove the missing information we have no more information about the cancellations 
```{r}

CancelledSubset = subset(df.train, CancellationCode != 'N')
df.train$CancellationCodebyname <- df.train$CancellationCode 

df.train$CancellationCodebyname[df.train$CancellationCodebyname == 'A'] = 'Carrier'
df.train$CancellationCodebyname[df.train$CancellationCodebyname == 'B'] = 'Weather'
df.train$CancellationCodebyname[df.train$CancellationCodebyname == 'C'] = 'NAS'
df.train$CancellationCodebyname[df.train$CancellationCodebyname == 'D'] = 'Security'

```
```{r}

ggplot(CancelledSubset,aes(MonthByName,fill=CancellationCodebyname)) + geom_bar()



```

#### Draw the histogram 



```{r}
maxfer= nrow(df.train.complete)
par(mfrow = c(2,4) ); 
hist(df.train.complete$ArrDelay,          main = "Arrval Delay ", border = "blue", col = "light blue", breaks = 100)
hist(df.train.complete$DepDelay,          main = "Depart Delay ", border = "blue", col = "light blue", breaks = 100)
hist(df.train.complete$CarrierDelay,      main = "Carrier Delay", border = "blue", col = "light blue", breaks = 100)
hist(df.train.complete$WeatherDelay,      main = "Weather Delay.", border = "blue", col = "light blue", breaks = 100)
hist(df.train.complete$NASDelay,          main = "NAS Delay.", border = "blue", col = "light blue", breaks = 100)
hist(df.train.complete$SecurityDelay,     main = "Security Delay.", border = "blue", col = "light blue", breaks = 100)
hist(df.train.complete$LateAircraftDelay, main = "Late Aircraft Delay.", border = "blue", col = "light blue", breaks = 100)


```


```{r}
h0 <- hist(df.train.complete$ArrDelay,breaks=300, plot = FALSE)
h1 <- hist(df.train.complete$DepDelay,breaks=300, plot = FALSE) 

plot(h0, main = "Histogram of Arrival and Departure Delay ", col = rgb(0,0,1, alpha = 0.5), xlim = c(0,300))  #plot the first hist
plot(h1, col = rgb(1,0,0, alpha = 0.5), add = TRUE,xlim = c(0,300)) #add the second hist
legend("right", c( "Arrival Delay","Departure Delay"), fill = c("blue","red"), cex=0.8) #Legend

```

```{r}
library("limma")

hdnas<-logical(nrow(df.train.complete))
hdcar<-logical(nrow(df.train.complete))
hdwat<-logical(nrow(df.train.complete))
hdsec<-logical(nrow(df.train.complete))
hdlat<-logical(nrow(df.train.complete))

hdnas[which(df.train.complete$NASDelay>=15)]         =TRUE
hdcar[which(df.train.complete$CarrierDelay>=15)]     =TRUE
hdwat[which(df.train.complete$WeatherDelay>=15)]     =TRUE 
hdsec[which(df.train.complete$SecurityDelay>=15)]    =TRUE
hdlat[which(df.train.complete$LateAircraftDelay>=15)]=TRUE 

c5 <- cbind(hdnas, hdcar , hdwat , hdsec ,hdlat)


a <- vennCounts(c5)
vennDiagram(a, include = "both",
            names = c("NAS Delay", "Carrier Delay", "Weather Delay","Security Delay","Late Aircraft Delay"),
            counts.col = "red")
```
```{r}
num_of_NAS_only     = length(which(df.train.complete$NASDelay>=15 & df.train.complete$SecurityDelay==0 & df.train.complete$WeatherDelay==0 & df.train.complete$CarrierDelay ==0 & df.train.complete$LateAircraftDelay==0))
num_of_securit      = length(which(df.train.complete$NASDelay==0 & df.train.complete$SecurityDelay>=15 & df.train.complete$WeatherDelay==0 & df.train.complete$CarrierDelay ==0 & df.train.complete$LateAircraftDelay==0)) 
num_of_WeatherDelay = length(which(df.train.complete$NASDelay==0 & df.train.complete$SecurityDelay==0 & df.train.complete$WeatherDelay>=15 & df.train.complete$CarrierDelay ==0 & df.train.complete$LateAircraftDelay==0)) 
num_of_CarrierDelay = length(which(df.train.complete$NASDelay==0 & df.train.complete$SecurityDelay==0 & df.train.complete$WeatherDelay==0 & df.train.complete$CarrierDelay >=15 & df.train.complete$LateAircraftDelay==0)) 
num_of_LateAircraf  = length(which(df.train.complete$NASDelay==0 & df.train.complete$SecurityDelay==0 & df.train.complete$WeatherDelay==0 & df.train.complete$CarrierDelay ==0 & df.train.complete$LateAircraftDelay>=15)) 




slices <- c(num_of_WeatherDelay,num_of_NAS_only,num_of_securit ,num_of_CarrierDelay,num_of_LateAircraf)
lbls   <- c("Weather","NAS_only","Security","Carrier","Late Air craft")

pie(slices, labels = lbls, main="Pie Chart delay")
```
```{r}
non_char_list=which(lapply(df.train,typeof)!="character")
cor_list<-c(3,6,7,8,9,13,14,15,16,17,20,21,22)
pairs(sam.df.train.complete[as.numeric(cor_list)],col = "blue", cex = 0.5, upper.panel = NULL)
```



```{r}

ggplot(df.train.complete, aes(x=CRSElapsedTime, y=ActualElapsedTime))+geom_point(alpha=0.3, colour="blue")+geom_abline(colour="red", intercept=0, slope=1)
```


### Regretion 

```{r}

cor(df.train.complete$AirTime,df.train.complete$ActualElapsedTime)
rg_airTime_lm=lm(formula=df.train.complete$ActualElapsed~df.train.complete$AirTime)
summary(rg_airTime_lm)
```

```{r}
ggplot(df.train.complete, aes(x=AirTime, y=ActualElapsedTime))+geom_point(alpha=0.3, colour="blue")+geom_abline(colour="red", intercept= as.double(rg_airTime_lm$coefficients[1]), slope= as.double(rg_airTime_lm$coefficients[2]))
```
```{r}
cor(df.train.complete$AirTime,df.train.complete$Distance)
rg_airTime_lm=lm(formula=df.train.complete$AirTime~ df.train.complete$Distance)
summary(rg_airTime_lm)
```

```{r}
ggplot(df.train.complete, aes(x=Distance,y=AirTime))+geom_point(alpha=0.3, colour="blue")+geom_abline(colour="red", intercept= as.double(rg_airTime_lm$coefficients[1]), slope= as.double(rg_airTime_lm$coefficients[2]))

```

```{r}

var <- c("ActualElapsedTime","AirTime", "TaxiOut","TaxiIn")

toReg <- sam.df.train.complete[,var]
reg <- lm(ActualElapsedTime~., data= toReg)

summary(reg)
```
```{r}
df.train.complete <- df.train.complete[(df.train.complete$AirTime<750),]
df.train.complete <-df.train.complete[(df.train.complete$ArrDelay<400),]
summary(df.train.complete)

```
```{r}
cor(df.train.complete$AirTime,df.train.complete$ActualElapsedTime)
rg_airTime_lm=lm(formula=df.train.complete$ActualElapsed~df.train.complete$AirTime)
summary(rg_airTime_lm)
```
```{r}
ggplot(df.train.complete, aes(x=AirTime, y=ActualElapsedTime))+geom_point(alpha=0.3, colour="blue")+geom_abline(colour="red", intercept= as.double(rg_airTime_lm$coefficients[1]), slope= as.double(rg_airTime_lm$coefficients[2]))
```

### functions
```{r}
hist_all<-function(df,startIndex=1,endIndex=ncol(df))
{
  par(mfrow = c(2,4) )
  for( i in startIndex: endIndex)
  {
    hist(df[,i] ,main=colnames(df)[i],xlab = colnames(df)[i] ,border = "blue", col = "light blue", breaks = 100)  
  }
}
top_5_ori <-function (df)
{
  Origin.ord <- df[(df$Origin=="ORD"),]
  Origin.atl <- df[(df$Origin=="ATL"),]
  Origin.dfw <- df[(df$Origin=="DFW"),]
  Origin.ewr <- df[(df$Origin=="EWR"),]
  Origin.den <- df[(df$Origin=="DEN"),]
  return(list(Origin.ord,Origin.atl,Origin.dfw,Origin.ewr,Origin.den))
}
top_5_dest <- function(df)
{
  
  Dest.ord <- df[(df$Dest=="ORD"),]
  Dest.atl <- df[(df$Dest=="ATL"),]
  Dest.dfw <- df[(df$Dest=="DFW"),]
  Dest.ewr <- df[(df$Dest=="EWR"),]
  Dest.den <- df[(df$Dest=="DEN"),]
   return(list(Dest.ord,Dest.atl,Dest.dfw,Dest.ewr,Dest.den))
}
my_transform<-function(df)
{
  df.transformed <- data.frame(ArrDelay=df$ArrDelay,DepDelay.log=log(df$DepDelay),DepDelay=df$DepDelay,Distance=df$Distance,DayOfWeek=df$DayOfWeek,Month=df$Month,DepTime=df$DepTime)
  return(df.transformed)
}
my_ArrDelay_log_pow_lm<-function(df)
{
  temp_model<-lm(ArrDelay~DepDelay+DepDelay.log+DayOfWeek+Month+DepTime+I(DepDelay.log^2)+I(DepDelay^2),data=my_transform(df))
  return(temp_model)
}
my_ArrDelay_log_pow3_lm<-function(df)
{
  temp_model<-lm(ArrDelay~DepDelay+DepDelay.log+DayOfWeek+Month+DepTime+I(DepDelay.log^2)+I(DepDelay^2)+I(DepDelay.log^3)+I(DepDelay^3),data=my_transform(df))
  return(temp_model)
}
my_ArrDelay_log_lm<-function(df)
{
  temp_model<-lm(df$ArrDelay~df$DepDelay+df$DepDelay.log+df$DayOfWeek+df$Month+df$DepTime)
  return(temp_model)
}
my_ArrDelay_lm<-function(df)
{
  temp_model<-lm(df$ArrDelay~df$DepDelay+df$DayOfWeek+df$Month+df$DepTime)
  return(temp_model)
}

my_predict<- function(model,df.test) {
  y_est <- predict(model, my_transform(df.test))
  Res<- y_est - my_transform(df.test)$ArrDelay
  L1 <- sum(abs(Res))/length(Res)
  Res_sq<- Res^2
  RSS <- sum(Res_sq)
  MSE <- RSS/length(Res_sq)
  RMSE <- sqrt(MSE)
  return(data.frame(y_est=y_est,Res=Res,L1=L1,Res_sq=Res_sq,RSS=RSS,MSE=MSE,RMSE=RMSE))
}

hist_res<-function(temp)
{
  hist(as.data.frame(temp)$Res,border = "blue", col = "light blue", breaks = 100)
}
```
##### clean data

```{r}
df.train.complete.ori <- top_5_ori(df.train.complete)
df.train.complete.des <- top_5_dest(df.train.complete)
```
```{r}
 
par(mfrow = c(2,5) )
for(i in c(1:5))
  {
    hist(as.data.frame(df.train.complete.ori[i])$ArrDelay,border = "blue", col = "light blue", breaks = 100)
    hist(as.data.frame(df.train.complete.des[i])$ArrDelay,border = "blue", col = "light blue", breaks = 100)
  }
```
```{r}

model1 <- lm(df.train.complete$ArrDelay~df.train.complete$DepDelay)
summary(model1)

```
```{r}
plot(df.train.complete$DepDelay,df.train.complete$ArrDelay, cex=0.2)
abline(model1, col="blue")
```
```{r}
plot(model1)
```
```{r}
model2 <- lm(df.train.complete$ArrDelay~df.train.complete$DepDelay+log(df.train.complete$DepDelay))
summary(model2)

```

```{r}
plot(model2)
```
```{r}
model3 <- lm(df.train.complete$ArrDelay~df.train.complete$DepDelay+log(df.train.complete$DepDelay))
summary(model3)

```



```{r}
library(leaps) #This library enables to see all subsets
models <- regsubsets(ArrDelay~DepDelay+DepDelay.log+DayOfWeek+Month+DepTime+I(DepDelay.log^2)+I(DepDelay^2),data=my_transform(df.train.complete),nbest=10)



plot(models, scale = "r2")
```


```{r}
model_general_log=my_ArrDelay_log_lm(my_transform(df.train.complete))
summary(model_general_log)
plot(model_general_log)
```
```{r}
model_des_atl_log=my_ArrDelay_log_lm(my_transform(as.data.frame(df.train.complete.des[1])))
model_des_den_log=my_ArrDelay_log_lm(my_transform(as.data.frame(df.train.complete.des[2])))
model_des_dfw_log=my_ArrDelay_log_lm(my_transform(as.data.frame(df.train.complete.des[3])))
model_des_ewr_log=my_ArrDelay_log_lm(my_transform(as.data.frame(df.train.complete.des[4])))
model_des_ord_log=my_ArrDelay_log_lm(my_transform(as.data.frame(df.train.complete.des[5])))

model_general=my_ArrDelay_lm(df.train.complete)
model_des_atl=my_ArrDelay_lm(as.data.frame(df.train.complete.des[1]))
model_des_den=my_ArrDelay_lm(as.data.frame(df.train.complete.des[2]))
model_des_dfw=my_ArrDelay_lm(as.data.frame(df.train.complete.des[3]))
model_des_ewr=my_ArrDelay_lm(as.data.frame(df.train.complete.des[4]))
model_des_ord=my_ArrDelay_lm(as.data.frame(df.train.complete.des[5]))


model_ori_atl_log=my_ArrDelay_log_lm(my_transform(as.data.frame(df.train.complete.ori[1])))
model_ori_den_log=my_ArrDelay_log_lm(my_transform(as.data.frame(df.train.complete.ori[2])))
model_ori_dfw_log=my_ArrDelay_log_lm(my_transform(as.data.frame(df.train.complete.ori[3])))
model_ori_ewr_log=my_ArrDelay_log_lm(my_transform(as.data.frame(df.train.complete.ori[4])))
model_ori_ord_log=my_ArrDelay_log_lm(my_transform(as.data.frame(df.train.complete.ori[5])))

model_ori_atl=my_ArrDelay_lm(as.data.frame(df.train.complete.ori[1]))
model_ori_den=my_ArrDelay_lm(as.data.frame(df.train.complete.ori[2]))
model_ori_dfw=my_ArrDelay_lm(as.data.frame(df.train.complete.ori[3]))
model_ori_ewr=my_ArrDelay_lm(as.data.frame(df.train.complete.ori[4]))
model_ori_ord=my_ArrDelay_lm(as.data.frame(df.train.complete.ori[5]))


```
```{r}
model_general_log_pow=my_ArrDelay_log_pow_lm(my_transform(df.train.complete))
summary(model_general_log_pow)
plot(model_general_log_pow)
```
```{r}
model_general_log_pow3=my_ArrDelay_log_pow3_lm(my_transform(df.train.complete))
summary(model_general_log_pow)
plot(model_general_log_pow)
```
```{r}
df.test.complete  <- df.test [complete.cases(df.test ),]
df.test.complete.ori=top_5_ori(df.test.complete)
df.test.complete.des= top_5_dest(df.test.complete)
```


```{r}
pre_general <- my_predict(model_general, df.test.complete)
pre_general_log <- my_predict(model_general_log, my_transform(df.test.complete))
pre_general_log_pow<- my_predict(model_general_log_pow, my_transform(df.test.complete))

pre_des_atl_log<-my_predict(model_des_atl_log,my_transform(as.data.frame(df.test.complete.des[1])))
pre_des_den_log<-my_predict(model_des_den_log,my_transform(as.data.frame(df.test.complete.des[2])))
pre_des_dfw_log<-my_predict(model_des_dfw_log,my_transform(as.data.frame(df.test.complete.des[3])))
pre_des_ewr_log<-my_predict(model_des_ewr_log,my_transform(as.data.frame(df.test.complete.des[4])))
pre_des_ord_log<-my_predict(model_des_ord_log,my_transform(as.data.frame(df.test.complete.des[5])))


pre_des_atl<-my_predict(model_des_atl,as.data.frame(df.test.complete.des[1]))
pre_des_den<-my_predict(model_des_den,as.data.frame(df.test.complete.des[2]))
pre_des_dfw<-my_predict(model_des_dfw,as.data.frame(df.test.complete.des[3]))
pre_des_ewr<-my_predict(model_des_ewr,as.data.frame(df.test.complete.des[4]))
pre_des_ord<-my_predict(model_des_ord,as.data.frame(df.test.complete.des[5]))


pre_ori_atl_log<-my_predict(model_ori_atl_log,my_transform(as.data.frame(df.test.complete.ori[1])))
pre_ori_den_log<-my_predict(model_ori_den_log,my_transform(as.data.frame(df.test.complete.ori[2])))
pre_ori_dfw_log<-my_predict(model_ori_dfw_log,my_transform(as.data.frame(df.test.complete.ori[3])))
pre_ori_ewr_log<-my_predict(model_ori_ewr_log,my_transform(as.data.frame(df.test.complete.ori[4])))
pre_ori_ord_log<-my_predict(model_ori_ord_log,my_transform(as.data.frame(df.test.complete.ori[5])))

pre_ori_atl<-my_predict(model_ori_atl,as.data.frame(df.test.complete.ori[1]))
pre_ori_den<-my_predict(model_ori_den,as.data.frame(df.test.complete.ori[2]))
pre_ori_dfw<-my_predict(model_ori_dfw,as.data.frame(df.test.complete.ori[3]))
pre_ori_ewr<-my_predict(model_ori_ewr,as.data.frame(df.test.complete.ori[4]))
pre_ori_ord<-my_predict(model_ori_ord,as.data.frame(df.test.complete.ori[5]))
```
```{r}
list_pre_des_log= list(pre_des_atl_log,pre_des_den_log,pre_des_dfw_log,pre_des_ewr_log,pre_des_ord_log)
list_pre_des=list(pre_des_atl,pre_des_den,pre_des_dfw,pre_des_ewr,pre_des_ord)
list_pre_ori_log=list(pre_ori_atl_log,pre_ori_den_log,pre_ori_dfw_log,pre_ori_ewr_log,pre_ori_ord_log)
list_pre_ori=list(pre_ori_atl,pre_ori_den,pre_ori_dfw,pre_ori_ewr,pre_ori_ord)

rm(pre_den_atl_log,pre_des_den_log,pre_des_dfw_log,pre_des_ewr_log,pre_des_ord_log)
rm(pre_den_atl,pre_des_den,pre_des_dfw,pre_des_ewr,pre_des_ord)
rm(pre_ori_atl_log,pre_ori_den_log,pre_ori_dfw_log,pre_ori_ewr_log,pre_ori_ord_log)
rm(pre_ori_atl,pre_ori_den,pre_ori_dfw,pre_ori_ewr,pre_ori_ord)

```


```{r}
hist(as.data.frame(list_pre_des_log[1])$Res,main="ATL DEST LOG",border = "blue", col = "light blue", breaks = 100)
hist(as.data.frame(list_pre_des_log[2])$Res,main="DEF DEST LOG",border = "blue", col = "light blue", breaks = 100)
hist(as.data.frame(list_pre_des_log[3])$Res,main="DFW DEST LOG",border = "blue", col = "light blue", breaks = 100)
hist(as.data.frame(list_pre_des_log[4])$Res,main="EWR DEST LOG",border = "blue", col = "light blue", breaks = 100)
hist(as.data.frame(list_pre_des_log[5])$Res,main="ORI DEST LOG",border = "blue", col = "light blue", breaks = 100)
```
```{r}
hist(as.data.frame(list_pre_des[1])$Res,main="ATL DEST",border = "blue", col = "light blue", breaks = 100)
hist(as.data.frame(list_pre_des[2])$Res,main="DEF DEST",border = "blue", col = "light blue", breaks = 100)
hist(as.data.frame(list_pre_des[3])$Res,main="DFW DEST",border = "blue", col = "light blue", breaks = 100)
hist(as.data.frame(list_pre_des[4])$Res,main="EWR DEST",border = "blue", col = "light blue", breaks = 100)
hist(as.data.frame(list_pre_des[5])$Res,main="ORI DEST",border = "blue", col = "light blue", breaks = 100)
```

```{r}
hist(as.data.frame(list_pre_ori[1])$Res,main="ATL ORIGEN",border = "blue", col = "light blue", breaks = 100)
hist(as.data.frame(list_pre_ori[2])$Res,main="DEF ORIGEN",border = "blue", col = "light blue", breaks = 100)
hist(as.data.frame(list_pre_ori[3])$Res,main="DFW ORIGEN",border = "blue", col = "light blue", breaks = 100)
hist(as.data.frame(list_pre_ori[4])$Res,main="EWR ORIGEN",border = "blue", col = "light blue", breaks = 100)
hist(as.data.frame(list_pre_ori[5])$Res,main="ORI ORIGEN",border = "blue", col = "light blue", breaks = 100)
```

```{r}
hist(as.data.frame(list_pre_ori_log[1])$Res,main="ATL ORIGEN LOG",border = "blue", col = "light blue", breaks = 100)
hist(as.data.frame(list_pre_ori_log[2])$Res,main="DEF ORIGEN LOG",border = "blue", col = "light blue", breaks = 100)
hist(as.data.frame(list_pre_ori_log[3])$Res,main="DFW ORIGEN LOG",border = "blue", col = "light blue", breaks = 100)
hist(as.data.frame(list_pre_ori_log[4])$Res,main="EWR ORIGEN LOG",border = "blue", col = "light blue", breaks = 100)
hist(as.data.frame(list_pre_ori_log[5])$Res,main="ORI ORIGEN LOG",border = "blue", col = "light blue", breaks = 100)
```
```{r}
hist(pre_general$Res,main="GENERAL",border = "blue", col = "light blue", breaks = 100)
hist(pre_general_log$Res,main="GENERAL LOG",border = "blue", col = "light blue", breaks = 100)
hist(pre_general_log_pow$Res,main="GENERAL LOG",border = "blue", col = "light blue", breaks = 100)

```

```{r}
mean(as.data.frame(list_pre_ori_log[1])$L1)
mean(as.data.frame(list_pre_ori[1])$L1)
mean(as.data.frame(list_pre_ori_log[2])$L1)
mean(as.data.frame(list_pre_ori[2])$L1)
mean(as.data.frame(list_pre_ori_log[3])$L1)
mean(as.data.frame(list_pre_ori[3])$L1)
mean(as.data.frame(list_pre_ori_log[4])$L1)
mean(as.data.frame(list_pre_ori[4])$L1)
mean(as.data.frame(list_pre_ori_log[5])$L1)
mean(as.data.frame(list_pre_ori[5])$L1)
```
```{r}
mean(as.data.frame(list_pre_ori_log[1])$RMSE)
mean(as.data.frame(list_pre_ori[1])$RMSE)
mean(as.data.frame(list_pre_ori_log[2])$RMSE)
mean(as.data.frame(list_pre_ori[2])$RMSE)
mean(as.data.frame(list_pre_ori_log[3])$RMSE)
mean(as.data.frame(list_pre_ori[3])$RMSE)
mean(as.data.frame(list_pre_ori_log[4])$RMSE)
mean(as.data.frame(list_pre_ori[4])$RMSE)
mean(as.data.frame(list_pre_ori_log[5])$RMSE)
mean(as.data.frame(list_pre_ori[5])$RMSE)
```